### 2021-02-19 text/draft.tex
draft writing

An analysis of \texttt{keywords/keywords\_clean\_histogram.json} shows
that the distribution of keywords is strongly skewed right but that (see
Figure 3 for details).

@@

In what follows, I will describe how the cleaned keywords were
reconciled with Wikidata and YSO, and which additional steps for
refinement were undertaken. In total, 2'104 data transformation
operations were performed; the complete operation history is available
as \texttt{/keywords/operation\_history.json}. First
\texttt{keywords/keywords\_clean\_histogram.json} was set as a new
project in OpenRefine. The \texttt{keyword} column was then duplicated
and reconciled with Wikidata. Here the parameters were chosen as
follows: reconcile against no particular type, and auto-match candidates
with high confidence.

@@

!! Does the OpenRefine project still exist? Export the list of changes!

>>>>

An analysis of \texttt{keywords/keywords\_clean\_histogram.json} shows
that the lion's share of keywords has only one occurrence but that the
total occurrences are predominantly made up of keywords with more than
one occurrence (see Figure 3 for details).

@@

In what follows, I will describe how the cleaned keywords were
reconciled with Wikidata and YSO, and which additional steps for
refinement were undertaken. In total, 2'104 data transformation
operations were performed; the complete operation history is available
as \texttt{/keywords/operation\_history.json}.

A new project in OpenRefine was created and the data from
\texttt{keywords/keywords\_clean\_histogram.json} was imported. The
\texttt{keyword} column was then duplicated and reconciled with
Wikidata. Here the parameters were chosen as follows: reconcile against
no particular type, and auto-match candidates with high confidence.

There were X automatic matches (call them ``suggestions''). The quality
of these suggestions was then evaluated by random sampling. A suggestion
is considered to be correct if and only if the meaning of the keyword
from \texttt{keywords/keywords\_clean\_histogram.json} corresponds to
the meaning of the suggested subject term from Wikidata. Note that for
homonymous or polysemous keywords, it is impossible to confirm a correct
match without further context; those keywords therefore cannot be
reconciled (but see \protect\hyperlink{construction}{section
``Construction''} for a possible solution).

Unfortunately, random sampling showed that the overall quality of the
suggestions was not satisfactory. A two-pronged strategy was adopted to
ameliorate the quality of the reonciliation:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  manual matching of the top results
\item
  automated processes for the rest
\end{enumerate}

!! calculate for each of annif yso mesh how many percent of keywords or
total occurrences are covered by reonciliated data.

@@

!! Does the OpenRefine project still exist? Export the list of changes!
http://127.0.0.1:3333/project?project=2501403769019\&ui=\%7B\%22facets\%22\%3A\%5B\%7B\%22c\%22\%3A\%7B\%22type\%22\%3A\%22list\%22\%2C\%22name\%22\%3A\%22qid\%22\%2C\%22columnName\%22\%3A\%22qid\%22\%2C\%22expression\%22\%3A\%22isBlank(value)\%22\%2C\%22omitBlank\%22\%3Afalse\%2C\%22omitError\%22\%3Afalse\%2C\%22selectBlank\%22\%3Afalse\%2C\%22selectError\%22\%3Afalse\%2C\%22invert\%22\%3Afalse\%7D\%2C\%22o\%22\%3A\%7B\%22sort\%22\%3A\%22name\%22\%7D\%2C\%22s\%22\%3A\%5B\%5D\%7D\%5D\%7D
